\emph{icepack}: a new glacier flow modeling package in Python, version 1.0

### 2021-04-06 icepack.tex
More wordsmithing

Other fields with their own evolution equations can be a part of the problem as well as thickness and velocity.
The rheology and friction are the main coefficients in the diagnostic equation.
These coefficients are functions of other fields that have their own evolution equations.
For example, the rheology is a function of temperature, englacial water content, and damage from crevassing.
Likewise, the friction coefficient can be described in terms of the subglacial water pressure and a roughness factor for the underlying bedrock \citep{cuffey2010physics}.
The diagnostic and prognostic equations can then be supplemented with evolution equations for these fields, for example the heat equation for temperature, or a hydrology model for subglacial water pressure.

>>>>

The evolution equations for ice thickness and velocity are necessary for any simulation, both other fields with their own dynamics can be a part of the problem as well.
For example, the rheology and friction are the main coefficients in the diagnostic equation.
These coefficients are functions of other fields that have their own evolution equations.
The rheology is a function of temperature, englacial water content, and damage from crevassing.
Likewise, the friction coefficient can be described in terms of the subglacial water pressure and a roughness factor for the underlying bedrock \citep{cuffey2010physics}.
The diagnostic and prognostic equations can then be supplemented with evolution equations for these fields, for example the heat equation for temperature, or a hydrology model for subglacial water pressure.
